### 2022-08-28 latex/Chapters/DRLSearch.tex
update

It is quite fruitful to think of single-player, deterministic, fully-observable puzzles such as the \textbf{SP} and \textbf{RC} as unit-cost graphs. We start from an initial \textit{node} (usually some scrambled configuration of the \textbf{SP} or \textbf{RC}), and via legal moves, we transition to new nodes, until hopefully we manage to get to the goal in the shortest number of moves possible. 
\\
\\
Graph search (or graph traversal) is a rather large, sophisticated and mature branch of \textbf{CS} that studies strategies to find \textit{optimal} paths from initial to goal node in a graph. What is meant by \textit{optimal} can vary, but usually is concerned with one or several of minimizing the run-time of the strategies, their memory complexity/usage or the total cost/length of the solutions they come up with. In the general theory, different transitions can have different costs associated with them. Since each move of a tile in the \textbf{SP} or each rotation of a face in the \textbf{RC} might reasonably be thought as taking a constant and identical amount of time to perform, cost and length of solutions are one and the same, and I will therefore consider the graphs to be unit-cost (i.e. all transitions/moves cost 1).
\\
\\
Strategies typically maintain a frontier, which is the collection of unexpanded nodes so far. They keep expanding the frontier, by choosing the next node to expand (i.e. adding all the nodes reachable via legal transitions from that node) until a solution is found. The question is how to choose the next node to expand! Some graph search strategies are said to be uninformed, in the sense that they do not exploit any domain-specific knowledge or insight about what the graphs represent to choose the next node to expand. In that category fall for instance Breadth First Search (\textbf{BFS}) and Depth First Search (\textbf{DFS}), which as their name suggest expand nodes from the frontier based on, respectively, a \textbf{FIFO} and \textbf{LIFO} policy. \textbf{BFS} and \textbf{DFS} will only work for small problems where the number of transitions and states are reasonably small; they can however work on a wide variety of problems. It is quite easy to see that \textbf{BFS} is an \textit{optimal} search strategy, in that when it does find a solution, that solution is of smallest possible cost. \textbf{DFS} is obvisouly not.
\\
\\
Informed strategies on the other hand exploit domain-specific knowledge. One very popular such strategy is \textbf{A$^{*}$} (see \cite{DBLP:journals/jacm/DechterP85}), which always first examine the node of smallest expected total cost (\textbf{f}), itself the sum of the cost-so-far from initial to current node (\textbf{g}) plus the expected cost-to-go from current node to solution (\textbf{h}). The expected cost-to-go \textbf{h} is often called a \textit{heuristic}. The better the heuristic is, the better\textbf{A$^{*}$} usually performs. An important property of heuristics is \textit{admissibility}. In short, admissible heuristics never over-estimate the real cost-to-go, and can easily be shown to render\textbf{A$^{*}$} optimal.

@@

Quite similarly to \textbf{RL}, Deep Learning (\textbf{DL}) has not initially had the success the \textbf{AI} community was hoping it would. Marvin Minsky, who often took the blame for having \textit{killed} funding into the field, even regretted writing his 1969 book (\cite{minskypapert69}) in which he had proved that three-layer feed forward perceptrons were not quite the universal functions approximators some had hypothesied them to be. Since around 2006 (see \cite{GoodBengCour16}for more history of the recent burgeoning of \textbf{DL}), the field has known a rebirth, probably due to combination of factors, from ever more powerful computers and larger storage, the availability of data sets large and small on the internet, the advances in many techniques and heuristics (backward propagation, normalisation, drop-outs, etc..) and the huge amount of experimentation with different architectures (from very deep feed forward fully connected networks, to convolutional, recurrent and more exoctic networks). It is not an exageration to say that \textbf{DL} has rendered obsolete entire fields of research and bodies of knowledge e.g. in \textbf{CV} and \textbf{NLP}. \textbf{DL} has often become one of the methods of choice to learn of approximate highly dimensional functions. The beauty of it is that the relevant features that go into the function are autodiscovered by the training of the network, via back-ward propagation and trial-and-error, rather than having to be postulated or handcrafted as is often the case with other \textbf{ML} techniques.
\\
\\
For this project, I have implemented this in a class called DeepLearner (see section \ref{sec:codelearners} for details)

@@

So what is the link between all of these - A$^{*}$'s heuristics, \textbf{DL}, \textbf{RL}'s value iteration?
\\
\\
Sometimes we have ways of computing good solutions/heuristics to our puzzles, but cannot computationally do this for all possible states (maybe the state space is just too large!). One approach in that case is to compute the solution/heuristic for some states, and let a \textbf{DL} model learn how to extrapolate to the rest of the state space. This is a case of supervised learning in some sense, because we need a teacher-solver to tell us good solutions or heuristics.
\\
\\
An alternative approach in order to compute the cost-to-go is via \textbf{RL} value-iteration. Indeed, minimizing the cost-to-go (heuristic) is equivalent to maximising the cumulative reward given by -1 for each transition not reaching the goal state and +1 for the last transition to the goal. Clearly these two quantities are equivalent (modulo a trivial linear transformation). We can perform this value-iteration in an unsupervised way: we do not need a teacher to tell us the target value of the value function/cost-to-go but instead learn it simply from refining a state $s$'s value by replacing it at each iteration by the minimum of its current value, and the minimum value of all reachable states from $s$ polus one (since it takes one move to reach them). That is, for $t \in \mathbb{N}^{*}, s \in \mathcal{S}$, the state space, we update $V_{t}(s)$ via:
\begin{equation} \label{eq:DLVI}
V_{t+1}(s) \leftarrow min \Big( V_{t}(s), 1 + min_{s' \in \mathcal{C}(s)}(V_{t}(s'))  \Big)
\end{equation}
where $\mathcal{C}(s)$ are the children (reachable states via 1 move) of $s$
\\
The state space is often so large however, that we cannot practically perform this procedure for all states. This is where \textbf{DL} comes again to the rescue to act as function approximator, combining with \textbf{RL} into what has become known as \textbf{DRL}. The subtelty is then that both the left-hand-side and right hand side in the value-iteration procedure above are given by a \textbf{DL} network which we are constantly tweaking by back-ward propagation. For my implementation of \textbf{DRL}, I followed the same approach as in \cite{Mnih2013}, where the right hand-side of \ref{eq:DLVI} is a fixed \textit{target-network}. The left hand side is another \textit{current-network} which alone is modified by the \textbf{DL} learning (backward propagation and optimization), until convergence is deemed reached. We then update the \textit{target-network} by a copy of the \textit{current-network}, and then keep iterating again, until the whole process is deemed to have converged.
\\
\\
For this project, I have implemented this procedure in a class called DeepReinforcementLearner (see section \ref{sec:codelearners} for details)

>>>>

It is quite fruitful to think of single-player, deterministic, fully-observable puzzles such as the \textbf{SP} and \textbf{RC} as unit-cost graphs. We start from an initial \textit{node} (usually some scrambled configuration of the \textbf{SP} or \textbf{RC}), and via legal moves, we transition to new nodes, until hopefully we manage to get to the goal in the shortest number of moves possible. 
\\
\\
Graphs search (or graphs traversal) is a rather large, sophisticated and mature branch of \textbf{CS} that studies strategies to find \textit{optimal} paths from initial to goal node in a graph. What is meant by \textit{optimal} can vary, but usually is concerned with one or several of minimizing the run-time of the strategies, their memory complexity/usage or the total cost/length of the solutions they come up with. In the general theory, different transitions can have different costs associated with them. In this project however, we can reasonably consider that each move of a tile in the \textbf{SP} or each rotation of a face in the \textbf{RC} might are taking a constant and identical amount of time and effort to perform, and I will therefore consider all the graphs to be unit-cost (i.e. all moves have cost 1).
\\
\\
Search strategies typically maintain a frontier, which is the collection of unexpanded nodes so far. They keep expanding the frontier, by choosing the next node to expand (expanding a node simply means adding all of its children nodes - i.e. those which are reachable via legal transitions - to the frontier for future evaluation) until a solution is found. The question is how to choose the next node to expand! Some graphs search strategies are said to be \textit{uninformed}, in the sense that they do not exploit any domain-specific knowledge or insight about what the graphs represent to choose the next node to expand. In that category fall for instance Breadth First Search (\textbf{BFS}) and Depth First Search (\textbf{DFS}), which as their name suggest expand nodes from the frontier based on, respectively, a \textbf{FIFO} and \textbf{LIFO} policy. \textbf{BFS} and \textbf{DFS} will only work for modest problems where the number of transitions and states are reasonably small; they can however work in a wide variety of situations as they make no assumptions and require no knowledge. It is quite easy to see that \textbf{BFS} is an \textit{optimal} search strategy, in that when it does find a solution, that solution is of smallest possible cost (i.e. optimal). \textbf{DFS} is obvisouly not optimal as it could very well find a solution very deep in the graphs while expanding the very first branch, not realising that a solution was 1 level away from the start on another branch!
\\
\\
\textit{Informed} strategies, on the other hand, exploit domain-specific knowledge. One very popular such strategy is \textbf{A$^{*}$} (see \cite{DBLP:journals/jacm/DechterP85}), which always first examine the node of smallest expected total cost (\textbf{f}), itself the sum of the cost-so-far from initial to current node (\textbf{g}) plus the expected cost-to-go from current node to solution (\textbf{h}). The expected cost-to-go \textbf{h} is often called a \textit{heuristic}. The better the heuristic is, the better \textbf{A$^{*}$} usually performs. An important property of heuristics is \textit{admissibility}. In short, admissible heuristics never over-estimate the real cost-to-go, and can easily be shown to render \textbf{A$^{*}$} optimal.

@@

Quite similarly to \textbf{RL}, Deep Learning (\textbf{DL}) has not initially had the success the \textbf{AI} community was hoping it would. Marvin Minsky, who often took the blame for having \textit{killed} funding into the field, even regretted writing his 1969 book (\cite{minskypapert69}) in which he had proved that three-layer feed forward perceptrons were not quite the universal functions approximators some had hypothesized them to be. Since around 2006 (see \cite{GoodBengCour16} for more history of the recent burgeoning of \textbf{DL}), the field has known a rebirth, probably due to combination of factors, from ever more powerful computers and larger storage, the availability of data sets large and small on the internet, the advances in many techniques and heuristics (backward propagation, normalisation, drop-outs, different optimisation schemes, etc...) and the huge amount of experimentation with different architectures (from very deep feed forward fully connected networks, to convolutional, recurrent and more exoctic networks). It is not an exageration to say that \textbf{DL} has rendered obsolete entire fields of research and bodies of knowledge, most notably in \textbf{CV}, robotics, computational biology and \textbf{NLP}. \textbf{DL} has often become the method of choice to learn or approximate highly dimensional functions or random processes. The beauty of it is that the relevant features are autodiscovered during the training of the network, via back-ward propagation and trial-and-error, rather than having to be postulated or handcrafted as is often the case with other \textbf{ML} techniques.

@@

So what is the link between all of these - A$^{*}$'s heuristics, \textbf{DL}, \textbf{RL}'s value iteration?
\\
\\
Sometimes we have ways of computing good solutions/heuristics to our puzzles, but cannot computationally do this for all possible states (maybe the state space is simply too large!). One approach in that case is to compute the solution/heuristic for some states, and let a \textbf{DL} model learn how to extrapolate to the rest of the state space. This is a case of \textit{supervised} learning in some sense, since we need a teacher-solver to tell us good solutions or heuristics to extrapolate from.
\\
\\
An alternative approach in order to compute the cost-to-go is via \textbf{RL} value-iteration. Indeed, minimizing the cost-to-go (heuristic) is equivalent to maximising the cumulative reward given by -1 for each transition not reaching the goal state and +1 for the last transition to the goal. Clearly these two quantities are equivalent (modulo a trivial linear transformation). We can perform this value-iteration in an unsupervised way: we do not need a teacher to tell us the target value of the value function/cost-to-go but instead learn it simply from refining a state $s$'s value by replacing it at each iteration by the minimum of its current value, and the minimum value of all reachable states from $s$ polus one (since it takes one move to reach them). That is, for $t \in \mathbb{N}^{*}, s \in \mathcal{S}$, the state space, we update $V_{t}(s)$ via:
\begin{equation} \label{eq:DLVI}
\begin{split}
& V_{t+1}(s) \leftarrow min \Big( V_{t}(s), 1 + min_{s' \in \mathcal{C}(s)}(V_{t}(s'))  \Big) \\
& V_{t+1}(s) = 0 if s \in \mathcal{G}
\end{split}
\end{equation}
where $\mathcal{C}(s)$ are the children (reachable states via 1 move) of $s$ and $\mathcal{G}$ are the goal states.
\\
\\
The state space is often so large however, that we cannot practically perform this procedure for all states. This is where \textbf{DL} comes again to the rescue to act as function approximator, combining with \textbf{RL} into what has become known as \textbf{DRL}. The subtelty is then that both the left-hand-side and right hand side in the value-iteration procedure above are given by a \textbf{DL} network which we are constantly tweaking by back-ward propagation. For my implementation of \textbf{DRL}, I followed the same approach as in \cite{Mnih2013}, where the right hand-side of \ref{eq:DLVI} is a fixed \textit{target-network}. The left hand side is another \textit{current-network} which alone is modified by the \textbf{DL} learning (backward propagation and optimization), until convergence is deemed reached. We then update the \textit{target-network} by a copy of the \textit{current-network}, and then keep iterating again, until the whole process is deemed to have converged.
\\
\\
For this project, I have implemented this procedure in a class called DeepReinforcementLearner (see section \ref{sec:codelearners} for details)

### 2022-08-28 latex/Chapters/Implementation.tex
update

\chapter{Code} % Main chapter title

@@

\begin{landscape}
\begin{figure}[H]
\centering
\includegraphics[scale=0.49]{./Figures/codebase}
%\decoRule
\caption[Codebase]{Code base}
\label{fig:Codebase}
\end{figure}
\end{landscape}

@@

\item \textbf{PerfectHeuristic}: this reads from a data base the optimal costs, pre-computed by the PerfectLearner (see below \ref{PLcode})
\item \textbf{DeepLearningHeuristic}: this uses a network which has been trained using DRL by the DeepReinforcementLearner (see below \ref{DRLcode})
\end{itemize}

@@

\item \textbf{DeepLearner} tbd
\item \textbf{DeepReinforcementLearner}: It instantiates a DeepLearning (network), and trains it using DRL. It then saves the trained network, which can then be used in the DeepLearningHeuristic we have seen earlier in section \ref{HSS}. The DeepReinforcementLearner runs for a number of epochs (or less if, based on other parameters discussed below, it is deemed to have converged).

@@

\section{rubiks.solvers}
\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{./Figures/codebasesolvers}
%\decoRule
\caption[Codebase]{rubiks.solvers}
\label{fig:Codebasesolvers}
\end{figure}
This module implements solvers, which solve puzzles. The base class Solver is a Factory of solvers, and in addition to being able to instantiating the following types of solvers, can run different solvers through a similal sequences of random puzzles (for various increasing degrees of difficulty (shuffling), and/or perfectly shuffled ones) and display a comparison of how they perform in a number of metrics.

\begin{itemize}
\item \textbf{DFSSolver} TBD
\item \textbf{BFSSolver} TBD
\item \textbf{AStarSolver} TBD
\item \textbf{NaiveSlidingSolver} TBD
\item \textbf{Kociemba} TBD
\item \textbf{MonteCarloSearchTreeSolver} TBI I want to implement this in August when working on the Rubiks' ... following the Rubik's paper fromMcAleer \& Agostilenni et al \cite{https://doi.org/10.48550/arxiv.1805.07470}
\end{itemize}

>>>>

\chapter{Implementation} % Main chapter title

@@

\begin{landscape}
\begin{figure}[H]
\centering
\includegraphics[scale=0.40]{./Figures/codebase}
%\decoRule
\caption[Codebase]{Code base}
\label{fig:Codebase}
\end{figure}
\end{landscape}

@@

\item \textbf{PerfectHeuristic}: this reads from a data base the optimal costs, pre-computed by the PerfectLearner (see below \ref{PLcode})
\item \textbf{DeepLearningHeuristic}: this uses a network which has been trained using \textbf{DRL} by the DeepReinforcementLearner (see below \ref{DRLcode})
\item \textbf{DeepQHeuristic}: this uses a network which has been trained using \textbf{DQL} by the DeepQLearner (see below \ref{DQLcode})
\end{itemize}

@@

\item \textbf{DeepLearner} tbd
\item \textbf{DeepReinforcementLearner}: It instantiates a DeepLearning (network), and trains it using \textbf{DRL}. It then saves the trained network, which can then be used in the DeepLearningHeuristic we have seen earlier in section \ref{HSS}. The DeepReinforcementLearner runs for a number of epochs (or less if, based on other parameters discussed below, it is deemed to have converged). 
\item \textbf{DeepQLearner}: It instantiates a DeepLearning (network), and trains it using \textbf{DQL}. It then saves the trained network, which can then be used in the DeepLearningHeuristic as well as the DeepQHeuristic we have seen earlier in section \ref{HSS}. The DeepQLearner runs for a number of epochs (or less if, based on other parameters discussed below, it is deemed to have converged).

@@

\section{rubiks.solvers}
\label{sec:codesolvers}
\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{./Figures/codebasesolvers}
%\decoRule
\caption[Codebase]{rubiks.solvers}
\label{fig:Codebasesolvers}
\end{figure}
This module implements solvers, which solve puzzles. The base class Solver is a Factory of solvers, and in addition to being able to instantiating the following types of solvers, can run different solvers through a similal sequences of random puzzles (for various increasing degrees of difficulty (shuffling), and/or perfectly shuffled ones) and display a comparison of how they perform in a number of metrics.

\begin{itemize}
\item \textbf{DFSSolver} TBD
\item \textbf{BFSSolver} TBD
\item \textbf{AStarSolver} TBD
\item \textbf{NaiveSlidingSolver} TBD
\item \textbf{KociembaSolver} TBD
\item \textbf{MonteCarloSearchTreeSolver} TBI I want to implement this in August when working on the Rubiks' ... following the Rubik's paper fromMcAleer \& Agostilenni et al \cite{https://doi.org/10.48550/arxiv.1805.07470}
\end{itemize}

### 2022-08-28 latex/Chapters/SlidingPuzzle.tex
update

@@

As mentioned in chapter \ref{sec:Puzzles}, the state space cardinality for the SP grows very quickly with n and m. Here are the only dimensions which have less than 239.5 millions states. Note I am also only considering n $\leq$ m since (p, q) can always be solved if we know how to solve (q, p):
\\
\\
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 12 & 360 & 20,160 & 1,814,400 \\
3              &   &   & 181,440 &  &    \\
\end{tabular}
\end{center}
In this section, I will discuss \textbf{full} results for these 5 puzzles. In order to fully solve them, one can simply use rubiks.scripts.learner, setting up the PerfectLearner with A* and manhattan heuristic, or instantiate directly a PerfectLearner as have seen in section \ref{PLSS}
I obtained the following God numbers for these puzzles:
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 6 & 21 & 36 & 53* \\
3              &   &   & 31 &  &    \\
\end{tabular}
\end{center}
* provisional result
\\
\\
Notice that among the above dimensions, (n=2, m=5) is the largest and hardest one. I had to run its PerfectLearner over a couple of days, on a c5.18xlarge instance (72 cores) on Amazon EC2.
\\
\\
The perfectLearner also keeps track of (one of) the hardest puzzles it has encountered (i.e. requiring a number of steps equal to their respective God number to solves):
\\
\\
\underline{Most difficult 2x2 (6 moves)}:
\begin{center}
\begin{three}
\setrow{2}{,3}
\setrow{1}{2,1}
\end{three}
\end{center}
\underline{Most difficult 2x3 (21 moves)}:
\begin{center}
\begin{five}
\setrow{2}{4,5,}
\setrow{1}{1,2,3}
\end{five}
\end{center}
\underline{Most difficult 2x4 (36 moves)}:
\begin{center}
\begin{seven}
\setrow{2}{,7,2,1}
\setrow{1}{4,3,6,5}
\end{seven}
\end{center}
\underline{Most difficult 2x5 (53* moves)}:
\begin{center}
\begin{nine}
\setrow{2}{,4,9,2,1}
\setrow{1}{5,8,3,7,6}
\end{nine}
\end{center}
* provisional result
\\
\\
\underline{Most difficult 3x3 (31 moves)}:
\begin{center}
\begin{eight}
\setrow{3}{8,6,7}
\setrow{2}{2,5,4}
\setrow{1}{3,,1}
\end{eight}
\end{center}

@@

\newgeometry{top=0mm, bottom=0mm, left=0mm, right=0mm}
\begin{landscape}
\centering\vspace*{\fill}
\begin{figure}[H]
\centering
\includegraphics[align=c, scale=0.55]{./Figures/33SPDeepReinforcementLearning.jpeg}
\caption[33SPDeepReinforcementLearning]{Deep reinforcement learner 3x3 SP}
\label{fig:33SPDeepReinforcementLearning}
\end{figure}
\vfill
\end{landscape}
\restoregeometry

\subsection{Solvers' comparison}
\label{ssec:33SPSC}
Let me discuss a comparison of several algorithms on 1000 random puzzles generated for a number of random shuffling (with best-effort-no-backtracking) from 0 to 50 in step of 2, as well as for perfect shuffling (denoted by $\infty$) on the comparison graphs. The results are shown in figure \ref{fig:33SPPerformance}

@@

\begin{center}
\begin{tabular}{l*{5}{c}r}
\hline
\textbf{solver}      & & \textbf{cost} & \textbf{\# expanded nodes} & \textbf{run time (ms)} \\
\hline
AStarSolver[Manhattan]   &   &      31  & 58,859  & 11,327  \\
\hline
AStarSolver[PerfectHeuristic]  &   & 31 & 1,585 & 202 \\
\hline
AStarSolver[DeepLearningHeuristic]  &   & 31 & 101 & 58 \\
\hline
BFS  &   & - & - & time out \\
\hline
NaiveSlidingSolver  &   & 61 & n/a & 18 \\
\hline
\end{tabular}
\end{center}
On this specific configuration, there was obviously no chance that the BFS would complete, hence it timed out. It would have no matter what time out I set. Indeed, since it has no heuristic to guide its search, it would need to explore in the order of $3^{31}$ - roughly 617 trillions - nodes to reach the goal!
\\
Rather interestingly, my DRL heuristic performs much better than the manhattan heuristic (not super suprising), but also outperforms the perfect heuristic quite significantly both in terms of run time and of nodes expansion. Obviously there is no guarantee that the perfect heuristic will not be outperformed on some random configuration, and it does on this occasion. However, as we have seen in the previous subection \ref{ssec:33SPSC}, it is not the case on average.
\\
Finally, the naive solver outperforms every other solver in terms of run time, but finds a rather poor solution of 61 moves.

@@

%-----------------------------------
%	SECTION 4
%-----------------------------------

@@

>>>>

\begin{center}
\begin{tabular}{l*{9}{c}r}
\hline
\textbf{solver}      & & \textbf{Sliding Puzzle} & \textbf{2x2} & \textbf{2x3} & \textbf{2x4} & \textbf{2x5}  & \textbf{3x3} & \textbf{3x4} & \textbf{4x4} \\ 
\hline
BFS   & & & & & & &  x  & & \\
\hline
A$^{*}$[Manhattan]   & & & & & &  x  &  x  & & \\
\hline
A$^{*}$[Manhattan++]   & & & & & &  x  &  x  & & \\
\hline
A$^{*}$[Perfect]   & & &  x  &  x  &  x  &  x  &  x  & & \\
\hline
Naive   & & & & & & &  x  & & \\
\hline
A$^{*}$[DL[A$^{*}$[Perfect]]]   & & & & & & &  x  & & \\
\hline
A$^{*}$[DRL]   & & & & & & &  x  & & \\
\hline
A$^{*}$[DQL]   & & & & & & &  x  & & \\
\hline
MCTS[DQL][c=TBD]   & & & & & & &  x  & & \\
\end{tabular}
\end{center}

@@

As mentioned in chapter \ref{sec:Puzzles}, the state space cardinality for the SP grows very quickly with n and m. Here are the only dimensions which have less than 239.5 millions states. Note I am also only considering n $\leq$ m since (p, q) can always be solved if we know how to solve (q, p):
\\
\\
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 12 & 360 & 20,160 & 1,814,400 \\
3              &   &   & 181,440 &  &    \\
\end{tabular}
\end{center}
In this section, I will discuss \textbf{full} results for these 5 puzzles. In order to fully solve them, one can simply use rubiks.scripts.learner, setting up the PerfectLearner with A* and manhattan heuristic, or instantiate directly a PerfectLearner as have seen in section \ref{PLSS}. I obtained the following God numbers for these puzzles:
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 6 & 21 & 36 & 55* \\
3              &   &   & 31 &  &    \\
\end{tabular}
\end{center}
* provisional result
\\
\\
Notice that among the above dimensions, (n=2, m=5) is the largest and hardest one. I had to run its PerfectLearner over a couple of days, on a c5.18xlarge instance (72 cores) on Amazon EC2.
\\
\\
The perfectLearner also keeps track of (one of) the hardest puzzles it has encountered (i.e. requiring a number of steps equal to their respective God number to solves):
\\
\\
\underline{Most difficult 2x2 (6 moves)}:
\begin{center}
\begin{three}
\setrow{2}{,3}
\setrow{1}{2,1}
\end{three}
\end{center}
\underline{Most difficult 2x3 (21 moves)}:
\begin{center}
\begin{five}
\setrow{2}{4,5,}
\setrow{1}{1,2,3}
\end{five}
\end{center}
\underline{Most difficult 2x4 (36 moves)}:
\begin{center}
\begin{seven}
\setrow{2}{,7,2,1}
\setrow{1}{4,3,6,5}
\end{seven}
\end{center}
\underline{Most difficult 2x5 (55* moves)}:
\begin{center}
\begin{nine}
\setrow{2}{,9,3,7,1}
\setrow{1}{5,4,8,2,6}
\end{nine}
\end{center}
* provisional result
\\
\\
\underline{Most difficult 3x3 (31 moves)}:
\begin{center}
\begin{eight}
\setrow{3}{8,6,7}
\setrow{2}{2,5,4}
\setrow{1}{3,,1}
\end{eight}
\end{center}

@@

\newgeometry{top=0mm, bottom=0mm, left=0mm, right=0mm}
\begin{landscape}
\centering\vspace*{\fill}
\begin{figure}[H]
\centering
\includegraphics[align=c, scale=0.55]{./Figures/33SPDeepReinforcementLearning}
\caption[33SPDeepReinforcementLearning]{Deep reinforcement learner 3x3 SP}
\label{fig:33SPDeepReinforcementLearning}
\end{figure}
\vfill
\end{landscape}
\restoregeometry

\subsection{DRL vs DQL}

\subsection{MCTS DQL}

\subsection{Solvers' comparison}
\label{ssec:33SPSC}
Let me discuss a comparison of several algorithms on 1000 random puzzles generated for a number of random shuffling (with best-effort-no-backtracking) from 0 to 50 in step of 2, as well as for perfect shuffling (denoted by $\infty$) on the comparison graphs. The results are shown in figure \ref{fig:33SPPerformance}
\\
DL: 100 seq 15 to 31 shuffles 10k epochs connected 600 300 100
\\
Manhattan vs ++
\\
DQL vs DRL
\\
DxL vs Perfect

@@

\begin{center}
\begin{tabular}{l*{5}{c}r}
\hline
\textbf{solver}      & & \textbf{cost} & \textbf{\# expanded nodes} & \textbf{run time (ms)} \\
\hline
AStarSolver[Manhattan]   &   &      31  & 58,859  & 11,327  \\
\hline
AStarSolver[Manhattan++]   &   &      31  & 34,224  & 7,080  \\
\hline
AStarSolver[PerfectHeuristic]  &   & 31 & 1,585 & 202 \\
\hline
AStarSolver[DRLHeuristic]  &   & 31 & 101 & 58 \\
\hline
MCTSSolver[DQLHeuristic][c=0]  &   & 101 & 103 & 456 \\
\hline
MCTSSolver[DQLHeuristic][c=69]  &   & 35 & 2,244 & 8,873 \\
\hline
BFS  &   & - & - & time out \\
\hline
NaiveSlidingSolver  &   & 61 & n/a & 18 \\
\hline
\end{tabular}
\end{center}
On this specific configuration, there was obviously no chance that the BFS would complete, hence it timed out. It would have no matter what time out I set. Indeed, since it has no heuristic to guide its search, it would need to explore in the order of $3^{31}$ - roughly 617 trillions - nodes to reach the goal!
\\
Rather interestingly, my DRL heuristic performs much better than the manhattan heuristic (not super suprising), but also outperforms the perfect heuristic quite significantly both in terms of run time and of nodes expansion. Obviously there is no guarantee that the perfect heuristic will not be outperformed on some random configuration, and it does on this occasion. However, as we have seen in the previous subection \ref{ssec:33SPSC}, it is not the case on average.
\\
Finally, the naive solver outperforms every other solver in terms of run time, but finds a rather poor solution of 61 moves.

@@

\label{ssec:34SPSC}

\newgeometry{top=0mm, bottom=0mm, left=0mm, right=0mm}
\begin{landscape}
\centering\vspace*{\fill}
\begin{figure}[H]
\centering
\includegraphics[scale=0.63]{./Figures/34SPPerformance.jpeg}
%\decoRule
\caption[34SPPerformance]{Solvers' performance comparison 3x4 SP}
\label{fig:34SPPerformance}
\end{figure}
\vfill
\end{landscape}
\restoregeometry
%-----------------------------------
%	SECTION 4
%-----------------------------------

@@

\label{ssec:44SPSC}

\newgeometry{top=0mm, bottom=0mm, left=0mm, right=0mm}
\begin{landscape}
\centering\vspace*{\fill}
\begin{figure}[H]
\centering
\includegraphics[scale=0.63]{./Figures/44SPPerformanceAll.jpeg}
%\decoRule
\caption[44SPPerformance]{Solvers' performance comparison 4x4 SP}
\label{fig:44SPPerformance}
\end{figure}
\vfill
\end{landscape}
\restoregeometry
